Issues with Dynamical Measurements Across the Disk

### 2019-02-15 paper/ms.tex
Small fixes

We explore one science goal that relies on the conservation of actions --- the
reconstruction of open clusters across large distances using dynamical
tagging. The basic program is to match stars with roughly the same actions as
their supposed natal cluster. To set the scene, we consider the orbits of the
nine open clusters within $250\,\pc$ as reported by the {\em Gaia}
collaboration \citep{2018AA...616A..10G}. In Table~\ref{tab:real_clusters}, we
report the distance to each cluster, the three actions, and the maximum
vertical extent of their orbits ($z_{\text{max}}$). The actions are computed
using the technique described in Section~\ref{ssec:action_comp}. We also show
the mass of each cluster and the ``neighborhood'' we compute for each cluster,
which gives a rough sense of how far one can move away from the cluster before
the issue which we discuss next becomes important. This neighborhood is
discussed in more detail in Section~\ref{sssec:neighborhood}.

\begin{deluxetable*}{cCCCCCCC}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun, using the relevant initial positions and velocities from \citet{2018AA...616A..10G}.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} & \colhead{neighborhood} \\ 
\colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$} & \colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 & 352\tablenotemark{b} & 57 \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 & 410\tablenotemark{c} & 1460 \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 & 112\tablenotemark{d} & 522\\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 & 400\tablenotemark{e} & 462 \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 & & \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 & & \\
NGC2451A\tablenotemark{a} & 193.7 & 5.8 & -1805 & 0.21 & 73.4 & & \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 & 800\tablenotemark{f} & 685 \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9 & 550\tablenotemark{d} & 781
\enddata

>>>>

We explore one science goal that relies on the conservation of actions --- the
reconstruction of open clusters across large distances using dynamical
tagging. The basic program is to match stars with roughly the same actions as
their supposed natal cluster. To set the scene, we consider the orbits of the
nine open clusters within $250\,\pc$ as reported by the {\em Gaia}
collaboration \citep{2018AA...616A..10G}. In Table~\ref{tab:real_clusters}, we
report the distance to each cluster, the three actions, and the maximum
vertical extent of their orbits ($z_{\text{max}}$). The actions are computed
using the technique described in Section~\ref{ssec:action_comp}. We also show
the mass of each cluster and the ``neighborhood'' we compute for each cluster,
which gives a rough sense of how far one can move away from the cluster before
the issue which we discuss next becomes important. This neighborhood is
discussed in more detail in Section~\ref{sssec:reconstruction}.

\begin{deluxetable*}{cCCCCCCC}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun, using the relevant initial positions and velocities from \citet{2018AA...616A..10G}. The neighborhood column is explained in more detail in Section~\ref{sssec:reconstruction}.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} & \colhead{neighborhood} \\ 
\colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$} & \colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 & 352\tablenotemark{b} & 57 \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 & 410\tablenotemark{c} & 1460 \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 & 112\tablenotemark{d} & 522\\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 & 400\tablenotemark{e} & 462 \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 & & \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 & & \\
NGC2451A\tablenotemark{a} & 193.7 & 5.8 & -1805 & 0.21 & 73.4 & & \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 & 800\tablenotemark{f} & 685 \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9 & 550\tablenotemark{d} & 781
\enddata
